---
fig_height: 2.6
fig_width: 4
output:
  html_document:
    pandoc_args: [
      "+RTS", "-K16000m",
      "-RTS"
    ]
---

```{r, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Components of workflow

- Get data (acquisition)
- Modify data (cleaning)
- Analyze data (analysis)
- See data (visualization)
- Describe data (paper writing)

## Workflow 


```{r fig.width=8, fig.height=6,echo=FALSE}
library(png)
library(grid)
img <- readPNG("../images/r1.png")
grid.raster(img)
```

## Reproducibility

"Reproducibility is the ability of an entire analysis of an experiment or study to be duplicated, either by the same researcher or by someone else working independently."

(Wikipedia)

## How do we make our research reproducible?

- Everything must be documented.
- Everything must be automated.


## Workflow

```{r fig.width=8, fig.height=6,echo=FALSE}
library(png)
library(grid)
img <- readPNG("../images/r2.png")
grid.raster(img)
```

## Workflow

```{r fig.width=8, fig.height=6,echo=FALSE}
library(png)
library(grid)
img <- readPNG("../images/reproducible.png")
grid.raster(img)
```

## Want to know more about reproducible research?

Take this course (it's free)

https://www.coursera.org/learn/reproducible-research

## Rather than talk about it, let's do it



## Survey

https://goo.gl/forms/TbzlWnId64PoxNwA3

## Review results

## Think of a question

What is a research question you would like to answer, based on the data we've just produced?

```{r, echo = TRUE, eval = FALSE}
sex, fingers, age, happiness, siblings, hand, drinks, beauty, 
dancing, in_love, minutes_to_work, goat, mzn, money_or_sex,
describe_class, describe_self, describe_dream, 
donkeys_or_tennis_balls, minutes_since_laugh, ther_country, 
joe_or_brad, tattoos, describe_strength, describe_cism, 
prison_for_money, where_born, seconds_teeth, joe_kilos
```

## Practice

1. Open a markdown file. Save it as "survey_report.Rmd".

2. Make an introduction section using `#`

3. Write an introduction.

4. Include in your introduction the number of people who took the survey.

## Practice

3. Make an R chunk.

4. Go to www.databrew.cc/survey.R. Copy that code

5. Make an R chunk, paste the code.

## Practice

1. Make sections for other parts of your paper (methods, results, etc.).

2. Write at least one sentence in each section.

3. In the "Results" section, make a chart showing age.

4. In the "Results" section, make a chart showing sex.

5. In the "Results" section, make a chart addressing your research question.

## Cheatsheet

https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf