---
fig_height: 2.6
fig_width: 4
output:
  html_document:
    pandoc_args: [
      "+RTS", "-K16000m",
      "-RTS"
    ]
---

```{r, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Welcome Back !

These slides: 
http://www.databrew.cc/class2

## How was the homework?

```{r, echo = FALSE}
x <- -10:0
y <- c(rep(0, 5),
       1, 
       0, 
       1,
       1, 
       3,
       25)
plot(x, y, type = 'l',
     xlab = 'Days until homework due',
     ylab = 'Number of people asking for help')
```


### Review of rules

- Be on time (class starts at 15:00 exactly)
- Do your homework
- Ask for help

## Review

```{r}
frangos <- databrew::frangos
```

## Census {.build}

```{r}
census <- databrew::census
```


## Some questions

1. How many people in the data have a motorcycle.

2. Make a table called `floors` without the different types of floor materials.

3. Make a barplot of the `floors` table.

4. Make a dataframe of only those people without floors.

5. Make a map of only those people without floors.
