---
fig_height: 2.6
fig_width: 4
output:
  html_document:
    pandoc_args: [
      "+RTS", "-K16000m",
      "-RTS"
    ]
---

```{r, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Welcome Back !

These slides: 
http://www.databrew.cc/class2

## How was the homework?

```{r, echo = FALSE}
x <- -10:0
y <- c(rep(0, 5),
       1, 
       0, 
       1,
       1, 
       3,
       25)
plot(x, y, type = 'l',
     xlab = 'Days until homework due',
     ylab = 'Number of people asking for help')
```

## Comments on homework

- Use comments
- Send the R script
- It's okay to have problems.
- It's supposed to be hard!

## Difficulty

```{r, echo = FALSE}
x <- 1:10
y <- c(1:8, 4, 1)^2
plot(x, y,
     type = 'l',
     xlab = 'Level of difficulty',
     ylab = 'Amount of learning')
points(x = 8, y = 8^2,
       col = 'red')
```

## For next homework

- Ask for help!
- Ask early.
- Ask often.
- Ask by email.
- Include error messages.


## Review of rules

- Be on time (class starts at 15:00 exactly)
- Do your homework
- Ask for help

## Review

```{r}
library(databrew)
frangos <- databrew::frangos
```

## Census {.build}

```{r}
library(databrew)
library(cism)
census <- databrew::census
```


## Some questions

1. How many people in the data have a motorcycle.

2. Make a table called `floors` with the different types of floor materials.

3. Make a barplot of the `floors` table.

4. Make a dataframe of only those people without floors.

5. Make a map of only those people without floors.

## Some more questions

6. Make a map of _all_ people using `cism_map`, and color the map by the "floor_material" variable.

7. Make a map of only those people without floors, and color the map by the "sex" variable.

8. Make a table called `xt`. This will be a cross-table of the "moto" and "bike" variables.

9. Use `chisq.test` on the `xt` table to see if their is a significant correlation between having a motorcycle and having a bike.

