---
fig_height: 2.6
fig_width: 4
output:
  html_document:
    pandoc_args: [
      "+RTS", "-K16000m",
      "-RTS"
    ]
---

```{r, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Where is Joe {.build}

We're going to analyze where Joe is, using data from google. The data is part of the `databrew` package.

```{r}
# Load package
library(databrew)

# Get data
joe <- databrew::joe
```

## Where is Joe {.build}

Let's have a look at the structure of our data.

```{r, eval = TRUE}
head(joe)
```

## Where is Joe {.build}

Let's filter our data so that it only contains observations for the period from March 7-13.

```{r, eval = TRUE}
joe_filtered <- joe[joe$date >= '2017-03-07' &
                      joe$date <= '2017-03-13',]
```

## Where is Joe {.build}

Now let's use the `cism` package to plot Manhiça.

```{r, eval = TRUE}
library(cism)
library(sp)
library(maps)
manhica <- man3
plot(manhica)
```

## Where is Joe {.build}

The `databrew` package has a nice function called `visualize_location`. Let's try it out

```{r, eval = FALSE}
?visualize_location
```

## Where is Joe {.build}

```{r}
visualize_location(x = joe_filtered,
                   spdf = manhica)
```



## Where is Joe {.build}

Let's also try with an interactive map

```{r}
visualize_location(x = joe_filtered,
                   use_leaflet = TRUE)
```

## Some questions

1. Create an object called mar10. This will be the rows of `joe` which were on March 1, 2017.

```{r, echo = FALSE}
mar10 <- joe[joe$date == '2017-03-10',]
```

2. Make a map using `visualize_location` for where Joe on March 10, 2017.

```{r, eval = FALSE, echo = FALSE}
visualize_location(mar10)
```

3. Make a map using `cism_map` for where Joe was on March 10, 2017.

```{r, echo = FALSE, eval = FALSE}
cism_map_interactive(lng = mar10$longitude,
         lat = mar10$latitude)
```

4. Add a `spdf` and `popup` argument to `cism_map_interactive`.


```{r, echo = FALSE, eval = FALSE}
cism_map_interactive(lng = mar10$longitude,
         lat = mar10$latitude,
         spdf = man3,
         popup = mar10$time)
```
