---
title: "Homework 3"
author: "CISM Introductory R Course"
date: "Due: Tuesday, April 25, 2017 at 23:59"
fig_height: 2.6
fig_width: 4
output:
  html_document:
    pandoc_args: [
      "+RTS", "-K16000m",
      "-RTS"
    ]
    toc: true
    toc_float: true
    theme: united
---


```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, error= FALSE, cache = F}
# No scientific notation
options(scipen=999)

# Packages 
library(databrew)
library(stringr)
library(cism)
library(data.table)
library(dplyr)

# Basic knitr options
knitr::opts_chunk$set(comment = NA, 
               echo = TRUE,
               eval = FALSE,
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE)
```

This is homework assignment number 3. The assignment consists of creating an R script in this format: `Firstname_Lastname.R` (for example `Joe_Brew.R` with the code for the following problems. You must email that script to joebrew@gmail.com before 23:59 on Tuesday, April 25, 2017.

Make sure to use comments (`#`) in your code indicating which could refers to which sections/numbers. Also, given your answers below each question by also writing comments. 

If you run into any problems or have any questions, please email Joe.

## Section 1: Installation

We need to install some new packages (for next class). With a good internet connection, run the following.

```{r, eval = FALSE}
install.packages('ggthemes')
install.packages('gsheet')
```

If you installed these correctly, you should be able to run the following without errors.

```{r}
library(ggthemes)
library(gsheet)
```

## Section 2: Using `dplyr`

In this section, we're going to practice using the tools from the `dplyr` package. We'll be using weather data (which we also used in homework 2).

1. Run code to use the `databrew`, `cism` and `data.table` packages.

2. Get weather data for Maputo from 2010 to 2016 by running the following:

```{r}
# Get weather data
weather <- get_weather(station = 'FQMA', 
                       start_year = 2010,
                       end_year = 2017)
```

3. Create an object called `x`. This will be `weather`, but "arranged" by the `temp_max` variable. Hint, you'll need to use both `%>%` and `arrange`.

4. Delete x by using the `rm` command.

5. Create a new object called x. This will be `weather`, but it will have a new variable named `water`. Use `mutate` to create this variable. If `precipitation` is greater than 0, then `water` should say "wet day"; otherwise it should say "dry day". (Hint, you'll need to use `ifelse`)

6. Create an object called `y`. This will be `x`, then grouped by `water`, then summarise by creating a new variable called `number_of_days` which contains the number of days that were wet vs. dry. (Hint, you'll need to use `n()`)

7. Take a look at y. How many days were wet vs. dry?

8. Create an object called `z`. This will be `y`, but then `mutate` a new variable called `percentage_of_days`. This will be the `number_of_days` divided by the `sum(number_of_days)` multiplied by 100.

9. What percentage of days were wet in the dataset?

10. Now, you're going to _overwrite_ `weather` with itself (`weather <- weather`), but _then_ `mutate` a new variable called `too_hot_to_sleep`. This will be "yes" if the `temp_min` is greater than 28, and otherwise it will be "no". I'll help you on this one:

```{r}
weather <- 
  weather %>%
  mutate(too_hot_to_sleep = ifelse(temp_min > 28,
                                   "yes",
                                   "no"))
```

11. Create an object called `x`. This will be `weather`, grouped by our new variable (if it was too hot to sleep or not), and then `summarise`d to create a new variable called `number_of_days` which should be a simple count of whether it was too hot to sleep or not. In the same `summarise` function, also create a variable called `rain`, which should be the average `precipitation`.

```{r, echo = FALSE}
x <- weather %>%
  group_by(too_hot_to_sleep) %>%
  summarise(number_of_days = n(),
            rain = mean(precipitation))
```

12. Look at `x`. Which has more precipitation - days which were too hot to sleep or not?

13. Overwrite `weather` with `weather` again, but this time using `mutate` to create three variables: `year`, `month` and `day`. I'll help you on this one again.

```{r}
weather <- 
  weather %>%
  mutate(year = as.numeric(format(date, '%Y')),
         month = as.numeric(format(date, '%m')),
         day = as.numeric(format(date, '%d')))
```

14. Create an object called `x`. This will be `weather`, grouped by `year`, and then `summarise`d to get the following variables:
- `avgerage_temperature`: the mean of `temp_mean`
- `hottest_temperature`: the maximum of `temp_max`
- `lowest_temperature`: the minimum of `temp_min`
- `number_of_days`: the number of days

Whenever you use the `mean`, `max` or `min` functions, include `na.rm = TRUE` to make sure that the `NA` observations are removed. 

```{r, echo = FALSE}
x <- weather %>%
  group_by(year) %>%
  summarise(average_temperature = mean(temp_mean, na.rm = TRUE),
            hottest_temperature = max(temp_max, na.rm = TRUE),
            lowest_temperature = min(temp_min, na.rm = TRUE),
            number_of_days = n())
```

15. Make a plot showing the year on the x axis and the hottest temperature on the y axis. 

16. Overwrite `x` with itself, but use filter to keep only observations for which the year is less than 2016.

17. Make a plot showing the year on the x axis and the lowest temperature on the y axis, using the filtered data (`x`).

18. Create an object called `x`. This will be `weather`, then filtered to remove any days in 2017, then grouped by `month` and `day`, and then summarised to create a variable called `average_temperature` with the average temperature during that month

```{r, echo = FALSE}
x <- weather %>%
  filter(year < 2017) %>%
  group_by(month, day) %>%
  summarise(average_temperature = mean(temp_mean, na.rm = TRUE))
```

19. Overwite `x` with itself, but use `arrange` to order by `average_temperature`. 

20. Look at `x`. Which day of the year has the lowest average temperature?

## Section 3: Making a pretty plot

21. Don't worry, all you have to do is copy and paste here. If you can run the below code (and it produces a pretty plot), this means that (a) you successfully did the homework, and (b) you have all the packages you need for next class.

```{r, echo = TRUE}
library(ggplot2)
library(ggthemes)
ggplot(data = x,
       aes(x = factor(month),
           y = average_temperature)) +
  geom_jitter(alpha = 0.6) +
  geom_violin(fill = 'darkorange',
              alpha = 0.6) +
  labs(x = 'Month',
       y = 'Average temperature',
       title = 'Mozambican weather',
       subtitle = 'It is so lovely') +
  theme_economist()
```

Great work!