---
title: "Prevalence of Giardia lamblia in children under 5 years of age from Manhi?a."
author: "Augusto Messa Jr"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fig_height: 2.6
fig_width: 4
bibliography: bibliography.bib
output:
  html_document:
    toc: true
    toc_float: true
    theme: default
---


```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, error= FALSE, cache = F}
# No scientific notation
options(scipen=999)

# Packages 
library(databrew)
library(cism)
library(dplyr)
library(ggplot2)
library(ggthemes)
library(ggmap)
library(gsheet)
library(readr)
library(knitr)

# Options for this document (ie, whether to show code, errors, etc.)
knitr::opts_chunk$set(comment = NA, 
               echo = FALSE,
               eval = TRUE,
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE)

# Read in some data here
if(!'fexam_data.csv' %in% dir()){
  fexam_data <- gsheet2tbl('https://drive.google.com/open?id=1mx8hRRQlQ_HmZcbUuyZY0fuDhufBW0ITFqRUG7LkE00')
  write_csv(fexam_data, 'fexam_data.csv')
} else {
  fexam_data <- read_csv('fexam_data.csv')
}

fexam_datacases <- fexam_data %>% filter(case == "Cases")

fexam_datacontrols <- fexam_data %>% filter(case == "Controls")

```

# Introduction

Diarrhea is curently one of the biggest public health problems in the world, especially in developing countries. It is the second most important cause of mortality in children under 5 and is among the major morbidity and mortality causes around the world [@Zebardast2016]. In Mozambique it is the 3rd and 4th cause of children mortality in Maputo and Manhi?a, respectively, and in the latter diarrhea also accounts for up to 20% of the total children hospital admissions [@Dgedge2001, @Sacarlal2009, @Sacoor2013].

Previous studies in Manhi?a have shown that diarrhea in children under 5 is mainly caused by Rotavirus, Cryptosporidium spp., ST Enterotoxigenic Escherichia coli and Shigella spp. [@Mandomando2007, @Nhampossa2015]. The Global Enteric Multicenter Study, a case control in which Manhi?a was one of the sites, reported a high prevalence of infections by Giardia lamblia in both cases (children with diarrhea) and contrlols (assymptomatic children), but no comparison between this groups was made [@Nhampossa2015].

G. lamblia is one of the parasites with a global distribution (along with Cryptosporidium parvum), occuring in all climates and countries [@Caccio2005 , @Hill2011]. This parasite is the etiological agent of giardiasis, a disease which affects over 200 million people in Africa, Asia and Latin America, with about 500 thousand new cases reported yearly and being responsible for almost 2.5 million deaths in children [@Savioli2006, @Halliez2013, @JerezPuebla2015, @Minetti2015].

Children are by far the most afected group, because giardisis causes a wide range of abnormalities and consequences (e.g.: growth, development and cognitive impairment and deficits) in their physiology, resulting from the effects on their nutrition (e.g.: nutrient malabsorption, changes in the intestinal epithelium) [@Hill2011, @Halliez2013, @JerezPuebla2015]. This is most significative in developing countries where almost all children under the age of 5 years, are infected by Giardia [@Robertson2010, @Hill2011, @Halliez2013].

This study aimed to determine the prevalence of infection by G.lamblia in  children  under the age of 5 years (59 months) from Manhi?a, a rural area of Southern Mozambique and to compare the situation between those with diarrhea - cases and those asymptomatic - controls.

# Methodology

The study was conducted at the Manhi?a Health Research Centre (Centro de Investiga??o em Sa?de de Manhi?a - CISM) between 2007 and 2012. This study site has previously been described [@Nhacolo2006, @Sacoor2013]. 

The subjects were recruited by an active surveillance to detect all children under 5 (59 months) with diarrhea (cases) who sought assistance within all the health facilities inside of CISM's Demographic Surveilance System - DSS coverage area, and for each index case, 1 to 3 community controls (paired with the index case by age, sex and neighborhood) as described by [@Kotloff2012].

The criteria for selection / exclusion (definition of Moderate to Severe Diarrhea - MSD), stool sampling techniques, data collection and laboratorial techniques was described elsewhere [@Kotloff2012, @Panchalingam2012]. The subjects were divided in 3 age groups (0-11 months, 12-23 months and 24-59 months) for purposes of analysis.

G. lamblia was detected from all stool samples by Enzyme-linked Imunnosorbent Assay - ELISA using the commercial kit Giardia IIT (TECHLAB?, Blacksburg, VA, USA; Catalog number: 30405) following the manufacturer's protocol.

All the data in this study was obtained after a verbal explanation and an informed consent was signed by the child's guardian and no personal information was used in the study.


# Results
##Subsection 1 - Participants in the study
During our study period we were able to recruit `r nrow(fexam_data)` subjects, of which `r nrow(fexam_datacases)` were cases and `r nrow(fexam_datacontrols)` were controls. Table 1 summarises the distribution of the participants recruited for our study.

```{r}
table1 <- fexam_data %>%
  group_by(case_age, case) %>% 
  summarise(subjects = n())

kable (table1, caption = "Table 1 - Study population groupings")  
```

The same data is summarised in plot 1.

```{r}
tablex <- fexam_data %>%
  group_by(case, case_age, gender) %>% 
  summarise(subjects = n())

ggplot(data = tablex,
       aes(x=case_age, y = subjects,
           fill = case))+
  geom_col(position = "dodge")+
  facet_wrap(~gender)+
  labs(x = "Age Group", y = "Number of Subjects",
       title ="Plot 1: Study population by study groups",
       subtitle = "How many subjects from each group were recruited?")+
  theme_economist()
```


##Subsection 2 - Giardia prevalences

The following plot shows the infection rate (prevalence) by G. lamblia detected in each age group, and makes a comparison between cases and controls for each group.

```{r}
tabley <- fexam_data %>% 
  group_by(case, case_age, pn36) %>% 
  summarise(subjects = n()) %>%
  arrange(case_age)

ggplot(data = tabley,
       aes(x=case, y = subjects,
           fill = pn36))+
  geom_col(position = "dodge")+
  facet_wrap(~case_age)+
  labs(x = "Age Group", y = "Number of Subjects",
       title ="Plot 2: Prevalence of Giardia lamblia infection",
       subtitle = "G. lamblia infection in children under 5 in Manhi?a")+
  theme_economist()
```

The numerical data (prevalences in %) is sumarrised in tables 3-5.

```{r}
table2 <- tabley %>%
  filter(case_age == "0-11 months") %>%
  mutate(total = sum(subjects, na.rm = TRUE), prevalence = (subjects/total)*100)

table3 <- tabley %>%
  filter(case_age == "12-23 months") %>%
  mutate(total = sum(subjects, na.rm = TRUE), prevalence = (subjects/total)*100)

table4 <- tabley %>%
  filter(case_age == "24-59 months") %>%
  mutate(total = sum(subjects, na.rm = TRUE), prevalence = (subjects/total)*100)

kable(table2, caption = "Table 2 - Prevalences of Giardia lamblia infection in children from 0 - 11 months", digits = 2)

kable(table3, caption = "Table 3 - Prevalences of Giardia lamblia infection in children from 12 - 23 months", digits = 2)

kable(table4, caption = "Table 4 - Prevalences of Giardia lamblia infection in children from 24 - 59 months", digits = 2)
```

The following plot shows the exact distribution of infection by G. lamblia in all study groups.

```{r}
ggplot(data = fexam_data,
       aes(x = case_age,
           y=pn36, color = case))+
  geom_jitter(alpha = 0.5)+
  facet_wrap(~gender)+
  theme_economist()+
  labs(x = "Age group",
       y = "G. lamblia infection",
       title = "Plot 3: Distribution of Giairdia lamblia infection",
       subtitle = "Who is infected by G. lamblia?")

```


##Subsection 3 - Other data 

This plot shows the relationship between the habit of storing vs treating the water. Those habits are compared based on how the stool (feces) were treated (destination).

```{r}
ggplot(data = fexam_data,
       aes(x = store_water,
           y=trt_water, color = pn36))+
  geom_jitter(alpha = 0.5)+
  facet_wrap(~disp_feces)+
  theme_economist()+
  labs(x = "Is the drinking water stored?",
       y = "Is the drinking water treated?",
       title = "Plot4: Association between behaviours and G. lamblia infection",
       subtitle = "What does stroring and treating water & different manure treatments do to the infection rate by G. lamblia?")
```


# Discussion

Giardia lamblia had previosly been detected in Mozambique by several studies conducted in Maputo (the country's capital city) [@Fonseca2009, @Fonseca2014, @Chilaule2016], in Manhi?a (a district in Maputo - Southern Mozambique) [@Nhampossa2015] and in Marrere (a locality in Nampula - Northern Mozambique) [@Guidetti2011].

In this study we had a higher detection rate of infection in assymptomatic children (controls) when compared to children which presented various clinical symptoms, from which the main was diarrhea (tables 2,3 and 4 & plots 2 and 3). This finding is consistent with those obtained from previous studies in various locations around the globe [@Hill2011, @Nunes2016], therefore it has been already established that prevalence of  infection by G. lamblia tends   to be higher in assympomatic people when compared to those presentic clinical symptoms  (e.g.: diarrhea and other gastrointestinal syndromes). This is particularly important for children, where there has been a description of cysts being shed during 6 months without any clinical syndrome [@Hill2011].

G. lamblia is transmited by the fecal-oral route, from direct contact with stool containing the cysts or trhough vehicles (mainly water, food, soil, etc. contaminated by stool) [@Hill2011, @Robertson2014]. This transmission route makes G. lamblia a problem, especially for developing countries (e.g.: Sub-saharan countries) where water access and management plus human manure treatment pose a serious problem to public health [@Halliez2013]. It is clear from the picture in plot 4, that the absence of water treatment is associated with a higher infection rate, specially when the water is stored regardless of the stool management in place. 

It is true that there weren't any statistical tests applied in this study, but the data gathered here calls our attention to look into this matter, specially because all data in here is from children under 5, one of the most vulnerable population groups. Other important thing that should also be evaluated in the future is the water sources usedby these populations.


# References
