---
title: "Homework 4"
author: "CISM Introductory R Course"
date: "Due: Monday, May 8, 2017 at 23:59"
fig_height: 2.6
fig_width: 4
output:
  html_document:
    pandoc_args: [
      "+RTS", "-K16000m",
      "-RTS"
    ]
    toc: true
    toc_float: true
    theme: united
---


```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, error= FALSE, cache = F}
# No scientific notation
options(scipen=999)

# Packages 
library(databrew)
library(stringr)
library(cism)
library(data.table)
library(dplyr)

# Basic knitr options
knitr::opts_chunk$set(comment = NA, 
               echo = TRUE,
               eval = FALSE,
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE)
```

This is homework assignment number 4. The assignment consists of creating an R script in this format: `Firstname_Lastname.R` (for example `Joe_Brew.R` with the code for the following problems. You must email that script to joebrew@gmail.com before 23:59 on Monday, May 8, 2017.

Make sure to use comments (`#`) in your code indicating which could refers to which sections/numbers. Also, given your answers below each question by also writing comments. 

If you run into any problems or have any questions, please email Joe.

## Section 1: Installation

As usual, we need to install some things before next class. **THIS WILL TAKE A LONG TIME**. Do not wait until the last minute.

### Installation of miscellaneous packages

Run the following code. If you get any errors (ie, you don't have the package), install that package. 

```{r, eval = FALSE, echo = TRUE}
library(knitr)
library(rmarkdown)
library(gsheet)
library(plotly)
```

If you installed these correctly, you should be able to run the above without errors.

### Installation of latex for creating pdfs in R

You need a good internet connection. Do NOT wait until the last minute to do this.

- If you have windows, go to http://ftp.sun.ac.za/ftp/CTAN/systems/win32/miktex/setup/basic-miktex-2.9.6326-x64.exe and download/install.

- If you have mac, download and install from this link: http://tug.org/cgi-bin/mactex-download/MacTeX.pkg

In some cases, the CISM network may block you from downloading things. If this is the case for you, you have two options:

1. Download from a different network.  
2. Send an email to Joe, who will install the program directly on your machine from a USB.

### Installation of prerequesites for R Markdown

- Open RStudio  
- Click "File" in the upper left  
- Click "New file"  
- Click "R Markdown"
- Change the title to "Test" and the author to your name  
- Click "PDF"  
- Click "OK"  
- Here, if you are asked to install anything, say yes  
- Now, in Rstudio, you have a document open called "Untitled1". 
- Click the "Knit" button at the top center of Rstudio.  
- It will ask you to save the file. Save it as "test".  


Did you generate a pdf? If yes, great, you're good to go. If not, write an email to Joe with your specific error/problem and I will help you.

## Section 2: Get inspired

This section is optional. If you answer the questions in the section, you can get some "extra credit" - but it is not required.

1. Watch this video.

<iframe width="640" height="360" src="https://www.youtube.com/embed/5Zg-C8AAIGg" frameborder="0" allowfullscreen></iframe>

2. Write in a comment in your code the main message of the video.

3. Find and write a link to a chart in an academic publication which you think is a _good_ data visualization. Why do you think it's good?

4. Find and write a link to a chart in an academic publication which you think is a _bad_ data visualization. Why do you think it's good?

## Section 3: Quick review of dplyr

I know, I know, you're sick of dplyr. But it's worth a little bit more practice.

1. Run the following code to get some data about cats.

```{r, echo = TRUE}
library(cism)
library(databrew)
library(dplyr)
cats <- MASS::cats
```

This data has three variables:

- Sex: the sex of the cat.  
- Bwt: the body weight of the cat.  
- Hwt: the heart weight of the cat.

2. Create an object called x, which shows the average body weight for each sex. Hint, you'll need to use `%>%`, `group_by` and `summarise`.

3. Which cats have a greater average body weight: males or females?

4. In `cats`, use `filter` to remove really fat cats (those with a `Bwt` of greater than 3.8 kilograms). (Hint, you'll need to use `cats <- cats %>% ...` to do this.)

5. In `cats`, use `mutate` to create a new variable called `hb`. This will be the heart weight divided by the body weight. (Hint, you'll need to use `cats <- cats %>% ...` to do this.)

6. Create an object called `x` which shows the average `hb` for each sex. 

7. Which cats have a greater average `hb` (heart to body weight ratio): males or females?

## Section 4: Data visualization

We're going to be make charts using `ggplot2` package. So, go ahead and run:

```{r, echo = TRUE}
library(ggplot2)
library(ggthemes)
library(MASS)
```

1. Get some data on traffic accidents by running the following code.

```{r, echo = TRUE}
traffic <- MASS::Traffic
```

2. Type `?Traffic` to get information on the dataset.

3. What do the variables mean?

4. Create a plot using `ggplot`. This will be of only one variable: `y`. Add a layer to make it a histogram

```{r, echo = FALSE}
ggplot(data = traffic,
       aes(y)) +
  geom_histogram()
```

5. Run the same code as above, but instead of a histogram, make a density chart.

```{r, echo = FALSE}
ggplot(data = traffic,
       aes(y)) +
  geom_density()
```

6. Run the same code as above, but add transparency, change the fill color, add a title, add an x label, and add a y label. 

```{r, echo = FALSE}
ggplot(data = traffic,
       aes(y)) +
  geom_density(fill = 'blue',
               alpha = 0.6) +
  labs(x = 'Accidents',
       y = 'Density')
```

7. Run the same code as above, but make the `fill` be different for whether or not there was a speed limit that day (ie, the `limit` variable).

```{r, echo = FALSE}
ggplot(data = traffic,
       aes(y,
           fill = limit)) +
  geom_density(alpha = 0.6) +
  labs(x = 'Accidents',
       y = 'Density')
```

8. Based on the above chart, did having a speed limit reduce the number of daily traffic accidents?

9. Create a new plot. This will have `limit` on the x axis and `y` on the y axis. Make it a jittered point chart (hint, use `geom_jitter`).

10. Run the same code as above, but add a boxplot to the chart. Make sure it's semi-transparent, so you can see the points.

11. Run the same code as above, but remove the boxplot and add a transparent violin chart.

12. Make the chart more beautiful by adding a theme, title, x label, and y label.

13. Run the same code as above, but use `facet_wrap` to create separate visualizations for each year.

```{r, echo = FALSE}
ggplot(data = traffic,
       aes(x = limit,
           y = y)) +
  geom_jitter() +
  geom_violin() +
  facet_wrap(~year)
```

14. Create an object called `daily`. This will be `traffic`, then grouped by day and limit, and then summarised to create a variable called `accidents` which will be the average number of accidents (`y`) on that day.

```{r, echo = FALSE}
daily <- traffic %>%
  group_by(day, limit) %>%
  summarise(accidents = mean(y))
```

15. Create a plot of `daily` with `day` on the x axis and `accidents` on the y axis. Make the `color` be a reflection of whether or not there was a `limit`. Add a layer of points.

```{r, echo = FALSE}
ggplot(data = daily,
       aes(x = day,
           y = accidents,
           color = limit)) +
  geom_point()
```

16. Run the same code as above, but add `geom_smooth()` to create smoothed trend lines.

```{r, echo = FALSE}
ggplot(data = daily,
       aes(x = day,
           y = accidents,
           color = limit)) +
  geom_point() +
  geom_smooth()
```

17. Make the chart beautiful.

18. Assign the code from the chart to an object named `g` like this

```{r, eval = FALSE, echo = TRUE}
g <- your_code_for_making_the_plot
```

19. Now run the following:

```{r}
library(plotly)
ggplotly(g)
```

20. Having now examined the data visually, if you were the president of Sweden, would you have a speed limit or not? Why?