---
title: "Guns and roses"
author: "Augusto Nhabomba"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fig_height: 2.6
fig_width: 4
output:
  html_document:
    toc: true
    toc_float: true
    theme: cosmo
---


```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, error= FALSE, cache = F}
# No scientific notation
options(scipen=999)

# Packages 
library(databrew)
library(cism)
library(dplyr)
library(ggplot2)
library(ggmap)
library(gsheet)
library(readr)

# Options for this document (ie, whether to show code, errors, etc.)
knitr::opts_chunk$set(comment = NA, 
               echo = FALSE,
               eval = TRUE,
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE)

# Read in the data for the survey we took in class the other data
if(!'survey.csv' %in% dir()){
  survey <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1kCpmpVqD4tzkdGgyLQGVqeZG1sJoe2FwFJIxtDRsrb0/edit?usp=sharing')
  write_csv(survey, 'survey.csv')
} else {
  survey <- read_csv('survey.csv')
}
```

# Introduction

self motivation and happiness at work are critical conditiones for a high quality resutls.

# Methods

the research used standardized questonar for to address the relavant qualities aspects of the motivatin toward cism


# Results
## Sub-section 1
plot of love and happiness
```{r}
ggplot(data=survey,aes(happiness, fill = in_love))+geom_density()+facet_wrap(~sex)
```

plot of happiness
```{r}
ggplot(data=survey,aes(happiness))+geom_density()
```


plot of self_sentiment variable
```{r}
survey$self_sentiment <- score_sentiment(survey$describe_self)
ggplot(data = survey, aes(self_sentiment))+geom_density()
```

## Sub-section 2

association confidence and cism 

```{r}
survey$cism_sentiment <- score_sentiment(survey$describe_cism)
survey$self_sentiment <- score_sentiment(survey$describe_self)
ggplot(data = survey,
       aes(x = age,
           y = cism_sentiment)) +
  geom_point()+geom_smooth(method = 'lm')
```



# Discussion
happiness and self confidence was seen afected by age and time in year at CISM. this might be due to limited career progression oportunities. 

# Conclusion
taking together the results presented and discuss here we conclude that at cism people get less happier with time.