---
title: "Does the number of siblings a person has affect the Happiness level" 
author: "Bea Galatas"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fig_height: 2.6
fig_width: 4
output:
  html_document:
    toc: true
    toc_float: true
    theme: journal
---


```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, error= FALSE, cache = F}
# No scientific notation
options(scipen=999)

# Packages 
library(databrew)
library(cism)
library(dplyr)
library(ggplot2)
library(ggmap)
library(gsheet)
library(readr)
library(tidyr)
library(databrew)
library(ggmap)
library(wordcloud)
library(wordcloud2) 
library(gapminder)
library(googleVis)
library(ggthemes)
library(broom)

# Options for this document (ie, whether to show code, errors, etc.)
knitr::opts_chunk$set(comment = NA, 
               echo = FALSE,
               eval = TRUE,
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE)

# Read in the data for the survey we took in class the other data
if(!'survey.csv' %in% dir()){
  survey <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1kCpmpVqD4tzkdGgyLQGVqeZG1sJoe2FwFJIxtDRsrb0/edit?usp=sharing')
  write_csv(survey, 'survey.csv')
} else {
  survey <- read_csv('survey.csv')
}
```

# Introduction

This study evaluated wether the number of siblings that a person has affects his/her happiness. The hypothesis is that those who have more borthers and sisters are happier than those who do not have any. 

# Methods

We performed a survey among the `r nrow(survey)` participants of the R class done by Joe Brew at CISM.


# Results

## Socio-demographic Characteristics 

There were 13 Female and 8 Male students who took part in the survey. One participant did not identify him/herself of any gender (Figure 1)

Figure 1: 

```{r}
# This is an R comment

# This is some code to produce a barplot of sex 
ggplot(data = survey,
       aes(x = sex)) +
  geom_bar() 

```


The mean age of participants was `r mean(survey$age)`, with a minimum age of `r min(survey$age)` and a maximum of `r max(survey$age)` (Figure 2). 

Figure 2: 

```{r}
ggplot() + 
  geom_histogram(data=survey, 
                 aes(age), 
                 col="Grey", 
                 fill="black") + 
  labs(y="Frequency", 
       x="Age", 
       title="Age Distribution of Study participants")
```

The study participants came mainly from Spain, USA and Mozambique (Figure 3)

Figure 3: 

```{r}
  places_of_birth <- geocode(survey$where_born,
                             output = 'latlon',
                             source = 'google',
                             messaging = TRUE)
  survey <- cbind(survey, places_of_birth)  

  world <- borders("world", colour="gray50", fill="gray50") # create a layer of borders
  ggplot() + 
    world +  
    geom_point(data=survey, 
               aes(x=lon, 
                   y=lat)) + 
    labs(title="Place of Birth of R Survey Participants", 
         y="Latitude", 
         x="Longitude") 
```

## Siblings Association

No association was observed between the number of siblings and the reported level of happiness (Figure 4).

Figure 4: 

```{r}
survey$siblings <- as.numeric(survey$siblings)
ggplot(data=survey, 
       aes(x=siblings, 
           y=happiness)) + 
  geom_jitter() + 
  geom_smooth()

```

# Discussion

This analysis identified that there was no significant association between the number of siblings a person has and the happiness index he/she reports. This study has some limitations bla bla bla... 

# Conclusion

This study is great although my question did not make much sense.
