---
title: "The Association between age and having tattoos"
author: "Delfino Vubil"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fig_height: 2.6
fig_width: 4
output:
  html_document:
    toc: true
    toc_float: true
    theme: lumen
---


```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, error= FALSE, cache = F}
# No scientific notation
options(scipen=999)

# Packages 
library(databrew)
library(cism)
library(dplyr)
library(ggplot2)
library(ggmap)
library(gsheet)
library(readr)

# Options for this document (ie, whether to show code, errors, etc.)
knitr::opts_chunk$set(comment = NA, 
               echo = FALSE,
               eval = TRUE,
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE)

# Read in the data for the survey we took in class the other data
if(!'survey.csv' %in% dir()){
  survey <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1kCpmpVqD4tzkdGgyLQGVqeZG1sJoe2FwFJIxtDRsrb0/edit?usp=sharing')
  write_csv(survey, 'survey.csv')
} else {
  survey <- read_csv('survey.csv')
}
```

# Introduction

This is a research paper about the association between age and having tattoos.

# Methods

There were `r nrow(survey)` participants in the survey.


# Results
This is a graphic of age distribution in the survey
```{r}

ggplot(data=survey, aes(x=age))+geom_bar()
```
Here is shown the number of males and females
```{r}

ggplot(data=survey, aes(x=sex))+geom_bar()
```
This figure shows the prevalence of right and left handed in the survey
```{r}

ggplot(data=survey, aes(x=hand))+geom_bar()
```

## Sub-section 1

We report that age is correlated with having tattoos.

```{r}
# This is an R comment

# This is some code to produce a barplot of sex 
ggplot(data = survey,
       aes(x =age, y=tattoos)) +
  geom_point() 
```

```{r}
ggplot(data = survey,
       aes(x = age)) +
  geom_density() +
  facet_wrap(~tattoos)

ggplot(data = survey,
       aes(x = age, fill=tattoos)) +
  geom_density(alpha=0.2) +
  theme_cism()

```


## Sub-section 2

# Discussion
There is a preference of tattoos in young people compared to older.  


# Conclusion
In summary, there is a possible correlation between age and having tattoos. Tattos were only reported in young people. 

