---
title: "Are people in love, happier?"
author: "Laia Cirera"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fig_height: 2.6
fig_width: 4
output:
  html_document:
    toc: true
    toc_float: true
    theme: journal
---


```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, error= FALSE, cache = F}
# No scientific notation
options(scipen=999)

# Packages 
library(databrew)
library(cism)
library(dplyr)
library(ggplot2)
library(ggmap)
library(gsheet)
library(readr)

# Options for this document (ie, whether to show code, errors, etc.)
knitr::opts_chunk$set(comment = NA, 
               echo = FALSE,
               eval = TRUE,
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE)

# Read in the data for the survey we took in class the other data
if(!'survey.csv' %in% dir()){
  survey <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1kCpmpVqD4tzkdGgyLQGVqeZG1sJoe2FwFJIxtDRsrb0/edit?usp=sharing')
  write_csv(survey, 'survey.csv')
} else {
  survey <- read_csv('survey.csv')
}
```

# Introduction

This is a research paper about a survey we took in class. It is written in Rmarkdown. Different questions were done to R students about different aspects of their lives, as well as perceptions and preferences. 

We want to find out whether being in love can be correlated to be happier, of whether it might be the oppositve, that single people enjoy from more freedom and thus, are happied. 


# Methods

There were `r nrow(survey)` participants in the survey.

We have looked at 2 variables of interest that were asked to all participants in the survey: 

1) Are you in love? Which the answer could be a) yes, b) no. 
2) How would you rate your happiness from 0 to 10 (being 10 the maximum value)?

# Results

## Sub-section 1

The graphs below, show the variables of interest in order to perform the analysis. 

In graph 1, you can see the distribution of happiness among R students, from 0 to 10.  

```{r}
ggplot(data = survey,
       aes(x = happiness)) +geom_histogram (color='black', fill='violet')+ labs(title='Graph 1. How happy are R students ?', subtitle='happiness density distribution', x='level of happiness', y='density level')  
```

In the following graph, you can observe the number of students that are in love or not: 

```{r}
ggplot(data = survey,
       aes(x = in_love)) +
  geom_bar (color='black', fill='red')+ labs(title='Graph 2. Are R students in love?', subtitle='distribution of people "in love"', x='are you i love?', y='number of students') 
```

It might be that our results differ on sex, given that men are more romantic and thus, can only achieve happiness when they are in real love (Brew,J. et al, 2017). In consequence, it might be worth to look a the age distribution among our sample in order to make sure the sex variable is well represented (graph 3).

```{r}
ggplot(data = survey,
       aes(x = sex)) +
  geom_bar(color='black', fill='blue')+ labs(title='Graph 3. R students sex distribution', x='are you male or female?', y='number of students') 
```

## Sub-section 2

The graph below (graph 4), shows us whether people that are in love tend to be happier or not.  

```{r}
ggplot(data=survey, aes(x=in_love, y=happiness)) + geom_jitter(alpha=0.5) +
  geom_violin(alpha=0) + labs(title='Graph 4. Does being in love make you happier?', x='are you in love?', y='degree of happiness') 

```

Finally, we want to verify whether it is more common for men to be happier when they are in love than it is with women: 

```{r}

ggplot(data=survey, aes(x=in_love, y=happiness, color=sex)) +
  geom_jitter(alpha=0.5) +
  geom_violin(alpha=0) +labs(title='Graph 5. Do men tend to relate more "being in love" to happiness than women?', x='are you in love?', y='degree of happiness') 
```
 
# Discussion

There exist important surveys around the world that show that "being in love" and "being happy" are tightly correlated. However, the present study doesn't show this and we observe that an important amount of students that are not in love are among the happiest. 

Moreover, We cannot test our hypothesis on whether man tend to relate more "being in love" with "being happy", as there isn't any women in the sample which is "not in love", and thus, we lack of evidence among this subsample of the population study. 

# Conclusion

Given that our results don't show the trends observed everywhere in the world, further research is needed in the area and additional surveys done within manhi?a R students population in order to be able to explain the factors that might drive their happiness. 