---
title: "Does age affect happiness"
author: "Lee Fonseca"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fig_height: 2.6
fig_width: 4
output:
  html_document:
    toc: true
    toc_float: true
    theme: simplex
---


```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, error= FALSE, cache = F}
# No scientific notation
options(scipen=999)

# Packages 
library(databrew)
library(cism)
library(dplyr)
library(ggplot2)
library(ggmap)
library(gsheet)
library(readr)

# Options for this document (ie, whether to show code, errors, etc.)
knitr::opts_chunk$set(comment = NA, 
               echo = FALSE,
               eval = TRUE,
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE)

# Read in the data for the survey we took in class the other data
if(!'survey.csv' %in% dir()){
  survey <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1kCpmpVqD4tzkdGgyLQGVqeZG1sJoe2FwFJIxtDRsrb0/edit?usp=sharing')
  write_csv(survey, 'survey.csv')
} else {
  survey <- read_csv('survey.csv')
}
```

# Introduction

In this work we will show how much age affects felecities.
# Methods

In the survey will include young people and adults between 18 and 45 years of age.


# Results
We find that less young people are emotionally happier in their relationship
```{r}
ggplot(data = survey,
       aes(x = age,
           y = in_love)) +
  geom_smooth(method = 'lm')

```

## Sub-section 1

Here is some more text.

```{r}
# This is an R comment

# This is some code to produce a barplot of sex 
ggplot(data = survey,
       aes(x = sex)) +
  geom_bar() 
```

## Sub-section 2

# Discussion

Why people feeling emotion when achieve 18 years old

# Conclusion
This survey aims to know the level of emotion of people in the early years of their youth.
