---
title: "My survey - Drinks and prison"
author: "Viviana Mabombo"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fig_height: 2.6
fig_width: 4
output:
  html_document:
    toc: true
    toc_float: true
    theme: journal
---


```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, error= FALSE, cache = F}
# No scientific notation
options(scipen=999)

# Packages 
library(databrew)
library(cism)
library(dplyr)
library(ggplot2)
library(ggmap)
library(gsheet)
library(readr)

# Options for this document (ie, whether to show code, errors, etc.)
knitr::opts_chunk$set(comment = NA, 
               echo = FALSE,
               eval = TRUE,
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE)

# Read in the data for the survey we took in class the other data
if(!'survey.csv' %in% dir()){
  survey <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1kCpmpVqD4tzkdGgyLQGVqeZG1sJoe2FwFJIxtDRsrb0/edit?usp=sharing')
  write_csv(survey, 'survey.csv')
} else {
  survey <- read_csv('survey.csv')
}
```

# Introduction

This survey explores the association of alcohol consumption in the last 7 days and the probability of going to prison for money (if oportunity arises).

# Methods

There were 19 participants in this survey, all of them had to respond to 30 questions.


# Results

## Sub-section 1

Distribution by sex.

```{r}
# This is an R comment

# This is some code to produce a barplot of sex 
ggplot(data = survey,
       aes(x = sex, fill = sex)) +
  geom_bar() 
```
Number of drinks consumed in the last 7 days, diferences between gender.

```{r}
ggplot(data = survey, aes(x = drinks, color = "red", fill = "purple"))+ geom_histogram(alpha = 0.5)+ theme_classic() + facet_wrap(~sex)
```





Number of people who would go to prison for money, and relation with alcohol consumption in the last 7 days.

```{r}
survey$drinks <- as.numeric(survey$drinks)
ggplot(data = survey, aes(x = drinks, fill = prison_for_money))+ geom_density(alpha = 0.5)
```
Relation between number of drinks in the last 7 days and going to prison for money. 
```{r}
ggplot(data = survey, aes(y = drinks, x = prison_for_money, color = prison_for_money, fill = prison_for_money))+ geom_boxplot(alpha = 0.5)+geom_point()
```

Relation between number of drinks in the last 7 days and going to prison for money, and diferences between gender.
```{r}

ggplot(data = survey, aes(y = drinks, x = prison_for_money, color = prison_for_money, fill = prison_for_money))+ geom_boxplot(alpha = 0.5)+geom_point()+facet_wrap(~sex)
```

## Sub-section 2

# Discussion

In the first chart, it is shown the number of participants distributed by sex (one participant could not tell in which group he/she belonged).in the second chart it is presented the number of drinks consumed in the last 7 days and the  diferences between gender.  
chart 3 shows a disturbing protection factor of alcohol for going to prison for money, therefore more analyses were made. 
Figure 4 and 5 show that there is a association between the number of drinks in the past 7 days and the risk of going to prison for money.

# Conclusion
Being male and drinking is a risk factor for going to prison for money. 