---
fig_height: 2.6
fig_width: 4
output:
  html_document:
    pandoc_args: [
      "+RTS", "-K16000m",
      "-RTS"
    ]
---

```{r, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Functions

It has 7 useful functions:

- `%>%`
- `arrange`
- `group_by`
- `mutate`
- `summarise`
- `select`
- `filter`

## Some comments

- A different syntax (less quotations, less dollar signs)
- Uses dataframes, more than variables
- Very fast


## `%>%`

This means "then".

```{r, eval = FALSE}
chicken %>%
  kill it %>%
  cook it %>%
  eat it
```

## `arrange` {.build}

## `group_by`  {.build}

## `mutate` {.build}

## `summarise` {.build}

## `select` {.build}

## `filter` {.build}

## Let's practice

I like animals. Let's get some data about them.

```{r}
animals <- MASS::Animals
```

## Some questions

1. Use `head` to see what our data looks like.

2. Create a plot with the `body` variable on the x-axis and the `brain` variable on the y-axis.

3. Create a variable called `name`. This will simply be the `row.names(animals)`.

4. Create an object called `animals`. This will be `animals` (over-write), but use `mutate` to divide `brain` by 1,000 in order to convert from grams to kilograms.

## Questions (continued)

5. Create an object called `animals`. This will be `animals` (over-write), but use `mutate` to create an object called `brain_to_body` which will be brain weight divided by body weight.

6. Create an object called `animals`. This will be `animals`, but use `arrange` to order by our new variable (`brain_to_body`).

7. Which animal has the greatest brain to body ratio? And the least?

## Questions (continued)

8. Use `mutate` to create a variable in `animals` which will be called `intelligence`. If the `brain_to_body` ratio is greater than 0.15, let's say "smart"; otherwise, let's say "stupid". Hint: use `ifelse`

9. Create an object called `x`. This will be `animals`, then `group_by` the `intelligence` variable, then use `summarise` to create two new variables: (1) the number of animals, and (2) the average body size of those animals.


## More practice

Let's get some data on birth weight.

```{r}
bw <- MASS::birthwt
```

## Questions on birthweight

1. Use `head` to look at our data.

2. Create a histogram to show the distribution of birthweight.

3. Create a plot showing the correlation between `age` (of mother) and the birth weight.

4. In `bw`, use `mutate` to create a new variable called `size`. If the birth weight is greater than 2500, call it "big"; otherwise, "small".

5. Create an object called `x`. This will be `bw`, then group by our `smoke` varible AND then use `summarise` to create a new variable called `average_grams` which will be the average birth weight.

6. What is the effect of smoking on birth weight?


## More practice

Let's get world bank data for Mozambique.

```{r}
library(cism)
library(dplyr)
wb <- cism::wb
```

## Some questions

1. Create an object called `phone`. This will be `wb` but `filter`ed so as to only include those rows where the `indicator_name` is "Mobile cellular subscriptions".

2. Make a plot of the number of of cell phone subscriptions.

3. Create an object called `mulungos`. This will be `wb` but `filter`ed so as to only include those rows where the `indicator_name` is ""International tourism, number of arrivals" AND the year is greater than 2000.

4. Make a plot of the number of tourists.

5. Run `sort(unique(wb$indicator_name))` to take a look at all the different data types in `wb`.

6. Pick one and plot it.

```{r, eval = FALSE, echo = FALSE}

5. Create an object called `gdp`. This will be `wb` but `filter`ed so as to only include those rows where the `indicator_name` is ""GDP per capita (constant 2010 US$)" AND the year is greater than 2000.

6. Make a plot of the GDP per capita over time.

```