---
title: "Survey report"
author: "R CISM class"
date: "May 10, 2017"
output: html_document
---

```{r setup, include=FALSE}
# Basic knitr options
knitr::opts_chunk$set(comment = NA, 
               echo = FALSE, 
               eval = TRUE,
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE)
```

```{r}
library(dplyr)
library(ggplot2)
library(ggmap)
library(gsheet)
library(cism)
library(databrew)
survey <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1kCpmpVqD4tzkdGgyLQGVqeZG1sJoe2FwFJIxtDRsrb0/edit?usp=sharing')
names(survey) <-
  c('time',
    'sex', 
    'fingers',
    'age',
    'happiness',
    'siblings',
    'hand',
    'drinks',
    'time_sleep',
    'time_wake',
    'beauty',
    'dancing',
    'in_love',
    'minutes_to_work',
    'goat',
    'mzn',
    'money_or_sex',
    'describe_class',
    'describe_self',
    'describe_dream',
    'donkeys_or_tennis_balls',
    'minutes_since_laugh',
    'ther_country',
    'joe_or_brad',
    'tattoos',
    'describe_strength',
    'describe_cism',
    'prison_for_money',
    'where_born',
    'seconds_teeth',
    'joe_kilos')

# Remove the fake rows
survey <-
  survey[6:nrow(survey),]

```

## Introduction

This is a paper that I wrote about the survey

## Research question

My research focuses on three important areas:

1. If money is more important than sex?

2. If my students are happy.

3. If students' collective perceptions reflect reality.

## Methodology

I made a silly survey and made my students fill it out. They were not provided with informed consent. This is not ethical.

## Results

### Money and sex

The below chart shows the distribution of happiness among CISM R students.

```{r}
ggplot(data = survey,
       aes(x = money_or_sex)) +
  geom_bar(alpha = 0.6) +
  theme_cism() +
  labs(x = 'Money or sex',
       y = 'People',
       title = 'Money or sex',
       subtitle = 'Which is more important?')
```

### Happiness

```{r}
ggplot(data = survey,
       aes(x = happiness)) +
  geom_density(alpha = 0.6,
               fill = 'darkblue') +
  theme_cism() +
  labs(x = 'Happiness',
       y = 'Density',
       title = 'Happiness',
       subtitle = 'Students of the CISM R course')
```

### Joe's weight

```{r}
ggplot(data = survey,
       aes(x = joe_kilos)) +
  geom_density(alpha = 0.6,
               fill = 'darkblue') +
  theme_cism() +
  labs(x = 'Kilograms',
       y = 'Density',
       title = 'The weight of Joe',
       subtitle = 'As perceived by students of the CISM R course')
```

## Secondary analysis: description of class


### Silly wordcloud

```{r}
library(wordcloud2)
library(dplyr)

# Break up the descriptions of class into individual words
words <- paste0(survey$describe_class, collapse = ' ')
words <- unlist(strsplit(words, ' '))
words_df <- data_frame(word = words)
words_df <- words_df %>%
  group_by(word) %>% 
  summarise(freq = n()) %>%
  data.frame
wordcloud2(data = words_df, size = 0.2)
```


```{r}
letterCloud(data = words_df, word = 'R')
```

### Sentiment analysis

```{r}
survey$sentiment <- databrew::score_sentiment(survey$describe_self)
```

```{r}
ggplot(data = survey,
       aes(x = sentiment)) +
  geom_density(aes(group = sex,
                   fill = sex),
               alpha = 0.6) +
  labs(x = 'Sentiment',
       y = 'Density',
       title = 'How do people describe themselves?',
       subtitle = 'Low = bad; high = good')
```