---
fig_height: 2.6
fig_width: 4
output:
  html_document:
    pandoc_args: [
      "+RTS", "-K16000m",
      "-RTS"
    ]
---

```{r, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


<!-- Getting data -->
## Getting data {.flexbox .vcenter}

We're going to use the `cism` package to get weather data for the `FQMA` weather station (Maputo).

```{r}
library(cism)
```

```{r, eval = FALSE}
??get_weather
```

## Getting data {.flexbox .vcenter}


```{r}
weather <- get_weather(station = 'FQMA', 
                       start_year = 2010,
                       end_year = 2016)
```

## Exploring data

Now that we have our weather data, we can look at it.

```{r, eval = FALSE}
head(weather)
```

## Exploring data

Now that we have our weather data, we can look at it.

```{r, eval = TRUE}
head(weather)
```



## Some questions on our data

1. How many rows are in our data?
2. How many columns?
3. What are the names of the columns?


## Some questions on our data

```{r, eval = FALSE}
# 1. How many rows are in our data?
nrow(weather)
# 2. How many columns?
ncol(weather)
# 3. What are the names of the columns?
colnames(weather)
```

## Some questions on our data

```{r, eval = TRUE}
# 1. How many rows are in our data?
nrow(weather)
```

## Some questions on our data


```{r, eval = TRUE}
# 2. How many columns?
ncol(weather)
```

## Some questions on our data

```{r, eval = TRUE}
# 3. What are the names of the columns?
colnames(weather)
```

## Questions about specific columns

4. What is the date range?
5. What is the maximum temperature?
6. What is the minimum temperature?
7. What is the average temperature?


## Questions about specific columns

```{r, eval = FALSE}
# 4. What is the date range?
range(weather$date)
# 5. What is the maximum temperature?
max(weather$temp_max)
# 6. What is the minimum temperature?
min(weather$temp_min)
# 7. What is the average temperature?
mean(weather$temp_mean)
```


## Questions about specific columns

```{r, eval = TRUE}
# 4. What is the date range?
range(weather$date)
```

## Questions about specific columns


```{r, eval = TRUE}
# 5. What is the maximum temperature?
max(weather$temp_max, na.rm = TRUE)
```

## Questions about specific columns

```{r, eval = TRUE}
# 6. What is the minimum temperature?
min(weather$temp_min, na.rm = TRUE)
```

## Questions about specific columns

```{r, eval = TRUE}
# 7. What is the average temperature?
mean(weather$temp_mean, na.rm = TRUE)
```

## Visualizing our data

Which variables do we have which are _numeric and continuous_?

How can we visualize these?

## Visualizing our data

Which variables do we have which are _numeric and continuous_?

* `temp_max`, `temp_mean`, `temp_min`, etc...

How can we visualize these?

* boxplot, histogram

## Boxplot

```{r}
boxplot(weather$temp_mean)
```

## Histogram

```{r}
hist(weather$temp_mean)
```

## Creating new variables

Let's create a variable called "hot"

## Creating new variables


```{r}
weather$hot <- ifelse(weather$temp_max > 30, 'hot', 'not hot')
```

## Creating new variables

```{r, eval = FALSE}
head(weather)
```

## Creating new variables

```{r, eval = TRUE}
head(weather)
```

## Exploring our new variable

```{r, eval = FALSE}
table(weather$hot)
hot_table <- table(weather$hot)
hot_prop_table <- prop.table(hot_table)
```


## Exploring our new variable

```{r, eval = TRUE}
hot_table <- table(weather$hot)
hot_prop_table <- prop.table(hot_table)
barplot(hot_table)
```

## Making our plot prettier {.smaller}


```{r, fig.height = 3}
barplot(hot_table,
        main = 'Hot days in Maputo')
```


## Making our plot prettier {.smaller}


```{r, fig.height = 3}
barplot(hot_table,
        main = 'Hot days in Maputo',
        ylab = 'Number of days')
```

## Making our plot prettier

```{r, fig.height = 3}
barplot(hot_table,
        main = 'Hot days in Maputo',
        ylab = 'Number of days',
        xlab = 'Temperature')
```

## Making our plot prettier {.smaller}

```{r, fig.height = 3}
barplot(hot_table,
        main = 'Hot days in Maputo',
        ylab = 'Number of days',
        xlab = 'Temperature',
        col = c('red', 'blue'))
```

## Making our plot prettier {.smaller}

```{r, fig.height = 3}
barplot(hot_table,
        main = 'Hot days in Maputo',
        ylab = 'Number of days',
        xlab = 'Temperature',
        col = c('red', 'blue'),
        border = 'darkgrey')
```

## Multi-variable plots

Let's create a plot of date (x-axis) and the maximum temperature

## Multi-variable plots

Let's create a plot of date (x-axis) and the maximum temperature

```{r, fig.height = 3}
plot(weather$date,
     weather$temp_max)
```


## Multi-variable plots

Let's make our plot prettier


## Multi-variable plots {.smaller}


Let's make our plot prettier

```{r, fig.height = 3}
plot(weather$date,
     weather$temp_max,
     type = 'l',
     col = 'red',
     xlab = 'Date',
     ylab = 'Maximum temperature',
     main = 'Maximim temperature in Maputo')
```
