---
params:
  email: beatriz.galatas@isglobal.org
title: "Mid-term report"
author: "CISM R Class"
date: "April 26, 2017"
output: pdf_document
---


```{r, echo = FALSE}
# Basic knitr options
knitr::opts_chunk$set(comment = NA, 
               echo = FALSE, 
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE)
```

```{r}
# Get data for class
# Libraries
library(mailR)
library(gsheet)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(cism)

file_name <- paste0('students_data_',
                    Sys.Date())
if(file_name %in% dir()){
  load(file_name)
} else {
  # Get data
  the_url <- 'https://docs.google.com/spreadsheets/d/1zz2OWpqG7TOtbEQNESj26LuYtRGfMt9Xrib6N5TMR_Y/edit?usp=sharing'
  students <- gsheet2tbl(the_url)
  save(students,
       file = file_name)
}

names(students) <-
  tolower(gsub(' ', '_', names(students)))
students <- data.frame(students)

# Get overall grade
hw_columns <- which(grepl('hw', names(students)) &
                      !grepl('comments', names(students)))
hw_columns <- names(students)[hw_columns]
students$overall <- NA
students$denom <- length(hw_columns) * 10
for (zz in 1:nrow(students)){
  this_persons_hw <-
    students[zz, hw_columns]
  students$overall[zz] <-
    sum(this_persons_hw)
  
}

# Get p
students$p <- students$overall / students$denom * 100
students$p <- round(students$p, digits = 2)

# Get the person
person <- students %>%
  filter(email_address == params$email)

# Get the  index
person_index <- which(students$email_address == params$email)
person_percentile <- round(percent_rank(students$p)[person_index] * 100)

# Get hws
hws <- person[,hw_columns]
hws <- data.frame(t(hws))
hws$number <- 1:nrow(hws)
row.names(hws) <- NULL
hws <- hws %>%
  rename(grade = t.hws.)
```

\begin{center}
\begin{LARGE}
`r paste0(person$first_name, ' ', person$last_name)`
\end{LARGE}
\end{center}

# Overall grade

\begin{large}
`r paste0(person$p, '%')`
\end{large}

As of `r Sys.Date()`, your overall grade is `r person$overall` out of `r person$denom`. This is equivalent to `r person$p`%.

# Comparison with rest of class

The below histogram shows the distribution of the grades of all `r nrow(students)` class students. The vertical red line shows the grade of `r paste0(person$first_name, ' ', person$last_name)`. This is equivalent to percentile `r round(person_percentile)`, which means that you are ahead of `r person_percentile`% of other students.

```{r, fig.height = 4}
ggplot(data = students,
       aes(x = p)) +
  geom_histogram(alpha = 0.6,
                 fill = 'darkblue') +
  theme_cism() +
  labs(x = 'Percent',
       y = 'Students',
       title = 'Comparison with other students',
       subtitle = paste0(person$first_name, ' vs. rest of class')) +
  geom_vline(xintercept = person$p,
             color = 'darkred')
```

# Specific HW grades

```{r, fig.height = 4}
ggplot(data = hws,
       aes(x = number,
           y = grade)) +
  geom_bar(stat = 'identity',
           alpha = 0.6,
           fill = 'darkgreen') +
  theme_cism() +
  labs(x = 'Assignment number',
       y = 'Score',
       title = 'Homework grades',
       subtitle = paste0(person$first_name, ' ', person$last_name)) +
  ylim(0, 12) +
  geom_hline(yintercept = 10, 
             lty = 2) +
  geom_label(aes(label = grade))
```

# Components of grade

As of now, your grade is composed of the `r length(hw_columns)` homework assignments only. The _final_ grade will be composed of 6 homework assignments plus a final exam score.

# How to improve your grade

There are two ways to improve your grade:

1. Do all future homework assignments on time.

2. If you missed any homework assignments, do them now to get credit.

# Details

The below table shows your homework grades and comments.

```{r}
x <- person[,grepl('hw', names(person))]
names(x) <- gsub('_', ' ', names(x))
pander::pander(x, keep.line.breaks = TRUE, justify = 'left')
```