---
title: "Final Exam"
author: "CISM Introductory R Course"
date: "Due: Friday, June 2, 2017 at 23:59"
fig_height: 2.6
fig_width: 4
output:
  html_document:
    pandoc_args: [
      "+RTS", "-K16000m",
      "-RTS"
    ]
    toc: true
    toc_float: true
    theme: united
---


```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, error= FALSE, cache = F}
# No scientific notation
options(scipen=999)

# Packages 
library(databrew)
library(stringr)
library(cism)
library(data.table)
library(dplyr)

# Basic knitr options
knitr::opts_chunk$set(comment = NA, 
               echo = TRUE,
               eval = FALSE,
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE)
```

# Overview

## Purpose of this exam.

This is your final exam. This exam has three purposes:

1. Combine all all learning from the last 3 months into one document.  
2. Contribute to your research output.   
3. Simulate "real life" by allowing collaboration and information-gathering.

## How the exam works

Your exam consists of writing a _complete research paper_. It doesn't need to be perfect, and it doesn't need to be long, but it needs to have all the components of good research. This means that it needs to fulfill some requirements:

### Requirements 

Your exam must contain: 

- A research question.
- Introduction, methodology, results, and discussion sections.
- At least 3 bibliographic references, cited in the paper.
- At least 3 charts.
- At least 1 table.

### Options

If you'd like you can do the following, but this is not required.

- Co-write your paper with one other person from the class.  
- Get help from Joe, classmates, the internet, etc.  
- Include more charts, tables, etc. than required.


## Three exam types

You have three options for this exam:

1. Use your OWN DATA. This is the best option, because it means that you can use this exam as the starting point for a paper that you will publish in 2017.

2. Use the data from the survey we took last class. If you choose this option, here is the code to read the survey data from the internet:

```{r, eval = FALSE, echo = TRUE}
# Read in the data for the survey we took in class the other data
if(!'survey.csv' %in% dir()){
  survey <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1kCpmpVqD4tzkdGgyLQGVqeZG1sJoe2FwFJIxtDRsrb0/edit?usp=sharing')
  write_csv(survey, 'survey.csv')
} else {
  survey <- read_csv('survey.csv')
}
```

3. Use the fake census data. To do this, you'll need to run the following code:

```{r, eval = FALSE, echo = TRUE}
census <- databrew::census
```

# Instructions

## Section 1: Getting set up

1. In RStudio, go to File -> New Project. Then select "New Directory" and then "Empty Project". Name the project "final_exam". Place the project/directory wherever you would like. Now close Rstudio.

2. Go to https://raw.githubusercontent.com/databrew/databrew.github.io/master/exam.Rmd, right click on the text and click "save as". Save the file in the folder you just created.

3. https://raw.githubusercontent.com/databrew/databrew.github.io/master/bibliography.bib, right click on the text and click "save as". Save the file in the folder you just created.

4. Open the folder you just created. You should have three files in there: "final_exam.Rproj", "exam.Rmd", and "bibliography.bib".

5. Double click on "final_exam.Rproj". This will open Rstudio. Now, in the bottom-right of RStudio, click on "Files" and then click on "exam.Rmd". This is the document you will do your exam in.

## Section 2: Reading in your data

1. At the bottom of the first R chunk in "exam.Rmd", read in your data. If you are doing exam type 2 or 3, this will be straightforward. If you are using your own data and you need help with this, ask Joe.

## Section 3: Write your paper

1. Each section (introduction, methodology, results, discussion) must have meaningful text.

2. All of your bibliographic references should have an entry in `bibliography.bib`, and should be referenced in your paper with code like: `[@Nhacolo2006]`. Use www.doi2bib.org to get your bibtex code to put in `bibliography.bib

That's it!


