---
title: "Homework 5"
author: "CISM Introductory R Course"
date: "Due: Monday, May 15, 2017 at 23:59"
fig_height: 2.6
fig_width: 4
output:
  html_document:
    pandoc_args: [
      "+RTS", "-K16000m",
      "-RTS"
    ]
    toc: true
    toc_float: true
    theme: united
---


```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, error= FALSE, cache = F}
# No scientific notation
options(scipen=999)

# Packages 
library(databrew)
library(stringr)
library(cism)
library(data.table)
library(dplyr)

# Basic knitr options
knitr::opts_chunk$set(comment = NA, 
               echo = TRUE,
               eval = FALSE,
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE)
```

This is homework assignment number 5. The assignment consists of creating two files:

1. Section 1: an R script in this format: `Firstname_Lastname.R` (for example `Joe_Brew.R` with the code for section 1). 

2. Section 2: an Rmarkdown file in this format: `Firstname_Lastname.Rmd` (for example `Joe_Brew.Rmd` with the code for section 2).

You must email the above two files to joebrew@gmail.com before 23:59 on Monday, May 15, 2017.

If you run into any problems or have any questions, please email Joe.

## Section 0: Installation

_For this section, you don't need to send me anything. Just make sure that to follow the steps so that your computer has all the correct / recent packages_

1. Re-install the "databrew" package. (We are doing this because the most recent version has the `score_sentiment` function for assessing the emotionality of written text.)

```{r}
remove.packages('databrew')
devtools::install_github('databrew/databrew')
library(databrew)
```

2. Make sure that you have the following packages installed as well: `ggmap`, `wordcloud`, `wordcloud2`, `gapminder`, `googleVis`. You can see if you have these by running the `library` function. If you don't have any of these packages, install them by using `install.packages`. 

If you have any installation problems, please email Joe.

Now you're done with section 2. You can delete all the code in this section (since it was only installation code).

## Section 1: Practice with survey data

### Section 1a. Review

1. Prepare your workspace by loading the following packages: `gsheet`, `dplyr`, `ggplot2`, `cism`, `ggmap`, `wordcloud2`, `ggthemes`, `readr`, and `databrew`.

2. Use the following code to download the survey data from the survey we took in class the other day.

(You'll need an internet connection for the first time you run this.)

```{r}
if(!'survey.csv' %in% dir()){
  survey <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1kCpmpVqD4tzkdGgyLQGVqeZG1sJoe2FwFJIxtDRsrb0/edit?usp=sharing')
  write_csv(survey, 'survey.csv')
} else {
  survey <- read_csv('survey.csv')
}
```

3. Use `table` to see how many people prefer money or sex. Write the anwer in a comment (ie, after a `#`).

4. Use `nrow` to see how many people took the survey. Write the answer in a comment.

5. Make a histogram of the age of the survey participants, using ggplot.

6. Make a barplot of the sex of the survey participants, using ggplot.

7. Make a density chart of the happiness of the survey participants, using ggplot.

8. Use the same code as number 7 (density chart of happiness), but facet it by sex.

9. Use the same code as number 7 (density chart of happiness), but make the `fill` of the density chart show whether or not the person is in love.

10. Use the same code as number 10, but make give it a title, subtitle, an x label and alpha.

### Section 1b. Spatial stuff

1. We have the `where_born` column which shows where people were born. But it's difficult to analyze because it's just words. We want to get the geo-locations of those words. This process is called "geocoding". Geocode the survey participants' place of birth by running the following code.

(You'll need an internet connection for this.)

```{r}
# Create an object for places of birth
places_of_birth <- geocode(survey$where_born,
                           output = 'latlon',
                           source = 'google',
                           messaging = TRUE)
```

2. Now you have an object called `places_of_birth`. Take a look at it by running `head(places_of_birth)`. What are the column names?

3. The word "bind" means "put together". We want to "bind" the columns of `places_of_birth` with our survey data. We can use the `cbind` function ("column bind") to do this. Run the following code:

```{r}
survey <- cbind(survey, places_of_birth)
```

4. Now run `head(survey)`. Do you have two new columns in the dataframe? What are their names?

5. Use ggplot to make a map of the world by running the following code.

```{r}
world <- borders("world", colour="gray50", fill="gray50") # create a layer of borders
ggplot() + world
```

6. Now use the same code from number 5, but add a layer of points from the survey.

7. Now use the same code as number 6, but make the size of those points show the age of the people.

8. Now use the same code as number 7, but make the color of the points show the sex of the people.

9. Now use the same code as number 8, but add a theme (for example `theme_cism()` or `theme_economist()`).

10. Now use the same code as number 10, but make the points a little bit transparent, add a title, a subtitle, and x / y labels.

### Section 1c. Analyzing free text

1. Make an object called `words`. This is going to be how many times each word was used in the `describe_cism` question of the survey. You can run the below code to do this.

```{r}
# Create an object called "words" which has how many times each
# word was used
words <- prepare_for_word_cloud(survey$describe_cism)
```

2. Take a look at the `words` object using `head`. What are the names of the columns?

3. Which word was used the most?

4. Run the following code to make a wordcloud.

```{r}
# Make the wordcloud of the object
wordcloud2(data = words, size = 0.3, shape = 'circle')
```

5. That's cool, right? But a bit hard to analyze. Let's use the `score_sentiment` function classify each the _emotion_ of each person's description of the the CISM. Create a variable called `cism_sentiment` in the `survey` dataframe. Use `score_sentiment` on the `describe_cism` variable to fill this new `cism_sentiment` variable.

(The `score_sentiment` function produces a score from -5 to 5. -5 is very negative, 5 is very positive, 0 is neutral.)

```{r, echo = FALSE}
survey$cism_sentiment <- score_sentiment(survey$describe_cism)
```

6. Make a density chart (using ggplot) of the new `cism_sentiment` variable.

```{r, echo = FALSE}
ggplot(data = survey,
       aes(x = cism_sentiment)) +
  geom_density()
```

7. Based on your plot, do people feel more negative or more positive towards the CISM?

8. Use `score_sentiment` to create a variable in `survey` called `self_sentiment`. For this variable, get the sentiment score of the `describe_self`.


```{r, echo = FALSE}
survey$self_sentiment <- score_sentiment(survey$describe_self)
```

9. Make a density chart of the new `self_sentiment` variable. 

```{r, echo = FALSE}
ggplot(data = survey,
       aes(x = self_sentiment)) +
  geom_density()
```

10. Based on your plot, do people feel more negative or more positive about themselves?

11. Make a scatterplot with `age` on the x-axis and `cism_sentiment` on the y-axis.

```{r}
ggplot(data = survey,
       aes(x = age,
           y = cism_sentiment)) +
  geom_point()
```

12. Add `geom_smooth(method = 'lm')` to the above scatterplot to put a line of best fit onto it.

13. Based on the above plot, do people feel more positive or less positive about the CISM as they get older?

## Section 2: Rmarkdown practice

1. Go to https://raw.githubusercontent.com/databrew/databrew.github.io/master/template.Rmd, right click on the text and "save as" to download the file there.

2. Save the file on your computer, but change the name of the file to `Firstname_Lastname.Rmd` (so, `Joe_Brew.Rmd`, for example).

3. Open the file and click the knit button. It should produce an html.

4. You'll notice that line 15 says `theme: united`. Change the theme to something else. You can see the possible themes at: http://rmarkdown.rstudio.com/html_document_format.html#appearance_and_style

5. Also change the `title:` and `author:` parameters to match a research question that interests you and _your_ name. This can be the research question from class the other day, or it can be something new. However, it must be from the survey. For example, the title can be "Does age affect happiness?" or "do people who are in love have more money in their pocket than people who are not in love?"

6. Now that you have changed the title, author, and theme, write a bit in the introduction and methods (just 2-3 sentences each).

7. In the results section, replace "Here is some more text" with something more interesting.

8. In the results section, add 3 more R chunks (Code -> Insert Chunk) with 3 plots of 3 different variables. At least 1 must be numeric, and at least 1 must be categorical.

9. Add text above each of your 3 plots.

10. Create one chart with multiple variables. This chart should address your research question.

11. Add text above your multiple variable chart.

12. Add some text to the "Discussion" and "Conclusion" sections.

13. Knit the whole document. 

Great work. You're done!