---
fig_height: 2.6
fig_width: 4
output:
  html_document:
    pandoc_args: [
      "+RTS", "-K16000m",
      "-RTS"
    ]
---

```{r, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Intro to dplyr

`dplyr` is the most useful package you will ever use.

```{r}
library(dplyr)
```

## Functions

It has 7 useful functions:

- `%>%`
- `arrange`
- `group_by`
- `mutate`
- `summarise`
- `select`
- `filter`

## Some comments

- A different syntax (less quotations, less dollar signs)
- Uses dataframes, more than variables
- Very fast

## Let's get some data to use

```{r}
library(databrew)
census <- databrew::census
```

## `%>%`

This means "then".

```{r, eval = FALSE}
chicken %>%
  kill it %>%
  cook it %>%
  eat it
```

## Arrange {.build}

Create an object called `x`. This will be the census, arranged by age.

```{r}
x <- census %>%
  arrange(age)
```


## Arrange {.build}

Create an object called `x`. This will be the census, arranged by `water_source`

```{r}
x <- census %>%
  arrange(water_source)
```


## Arrange {.build}

We can arrange by more than one variable.

Create an object called `x`. This will be the census, arranged by `floor_material`, `sex`, and `age`.


```{r}
x <- census %>%
  arrange(floor_material, sex, age)
```

## Arrange {.build}

Use arrange to find the age of the youngest person in the dataset.

## `group_by` and `summarise` {.build}

You always use `group_by` with other verbs, never by itself.

Example: Create an object called x. This will contain the average age for each sex.

```{r}
x <- 
  census %>%
  group_by(sex) %>%
  summarise(avg_age = mean(age))
```

## `group_by` and `summarise` {.build}

Create an object called x, with the minimum, maximum, and average age of people with pigs and people without pigs. Also, create a variable using `n()` for the number of people with and without pigs.

```{r}
x <- 
  census %>%
  group_by(pigs) %>%
  summarise(avg_age = mean(age),
            min_age = min(age),
            max_age = max(age),
            people = n())
```

## `group_by` and `mutate` {.build}

`mutate` is like `summarise`, but instead of creating a "summarical" dataset, it creates a new variable in the existing dataset.

For example, we can use it to get the average age for each sex

```{r}
x <- census %>%
  group_by(sex) %>%
  mutate(avg_age = mean(age))
```

## `select` {.build}

Useful for explicitly picking which columns you want to keep.

Example: create a dataset called `x` with only the age and sex columns.

```{r}
x <- census %>%
  select(age, sex)
```

## `select` {.build}

Create a dataset called `x` with all columns except for pigs.

```{r}
x <- census %>%
  select(-pigs)
```

## `filter` {.build}

Create a dataset called `x` with only people who have pigs.

```{r}
x <- census %>%
  filter(pigs == 'yes')
```

## `filter` {.build}

Create a dataset called `x` with only people who have pigs but don't have a telephone.

```{r}
x <- census %>%
  filter(pigs == 'yes',
         telephone == 'no')
```

## Questions

1. Create a dataset called x containing only people with cell phones.

2. Arrange x by age.

3. What is the 4th youngest age in x?

4. Create an object called y. This will be x, grouped by whether or not people have a bike. Use `summarise` and `n()` to get the number of people who have bikes and don't have bikes.

5. Create a new object called `z`. This will be the `census`, grouped by `sex` and `car`. Use `summarise` and `n()` to get the amount of people in each group and use `summarise` to get the average age of people in each group.



