---
fig_height: 2.6
fig_width: 4
output:
  html_document:
    pandoc_args: [
      "+RTS", "-K16000m",
      "-RTS"
    ]
---

```{r, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Get weather data

```{r}
library(cism)
library(data.table)
weather <- get_weather(station = 'FQMA', 
                       start_year = 2010,
                       end_year = 2017)
```

## Create a variable for month

```{r}
weather$month <- format(weather$date, '%m')
```

## Create a variable for year

```{r}
weather$year <- format(weather$date, '%Y')
```

## Introducing the `dplyr` package {.build}

`dplyr` is very useful

```{r}
library(dplyr)
```

## Get the average temperature per month

```{r}
x <- 
  weather %>%
  group_by(month) %>%
  summarise(average_temperature = mean(temp_mean, na.rm = TRUE))
```

## Visualization of average temperature

```{r}
plot(x = x$month,
     y = x$average_temperature)
```

## Questions

1. Create an object called `y`
2. In that object, group by monthand create variables called:
  - `max_temp` for max temperature
  - `min_temp` for min temperature
  - `rain` for total amount of precipitation

3. Make a plot of maximum temperature by month
4. Make a plot of minimum temperature by month
5. Make a plot of rainfall by month

## Grouping by multiple object
